The curious world of constructive mathematics

### 2023-04-11 algar-lecture-notes.tex
More work on the Brixen 2022a slides
Slides almost finished
to do

>>>>

completion of ℕ

Exercise: ∀∃ ⇒ Eventually

History of "AC ⇒ LEM":
1967 Bishop
1975 Douglas Bridges
1975 Diaconescu
1975 Anna Michaelides Penk
1978 Goodman and Myhill
2021 Andrew Swan, https://ncatlab.org/nlab/show/well-ordering+theorem

Cite: https://www2.mathematik.tu-darmstadt.de/~streicher/CLM/clm.pdf

Cite: https://www.mscsnet.mu.edu/~wim/publica/8802hist_print.pdf

https://www.math.ucla.edu/~joan/publicgothenburghandout.pdf
Peculiar characteristics of intuitionistic logic:
◮ (A → B) → ¬(A & ¬B) is provable, but the converse is not.
◮ ∃x¬A(x) → ¬∀xA(x) is provable, but the converse is not.
◮ ¬¬(A ∨ ¬A) is provable, but ¬¬∀x(A(x) ∨ ¬A(x)) is not.

Cite:
https://www.math.ucla.edu/~joan/newnotes.pdf

Cite:
https://arxiv.org/pdf/2102.01561.pdf
